\documentclass[11pt, letter, sans]{moderncv}
\linespread{1.4}
\usepackage[margin=.5in, bottom=0.5in, top=0.5in]{geometry}
\usepackage{setspace}
\usepackage{enumitem}
\pagestyle{empty}

\moderncvcolor{classic}
\name{Leon}{Chou}

\begin{document}
  \makecvtitle
  \begin{center}
    \textbf{{\LARGE Leon Chou}}\\
    1652 E 12 St Brooklyn, NY, 11229 \\
    leonchou123@gmail.com || 917 - 691 - 0038\\ www.github.com/bleepbloopsify\\
  \end{center}
  \noindent{\large \textbf{Education} }
  \vspace{0.1cm} \hrule \vspace{0.2cm}
  \noindent\textbf{New York University Tandon} : B.S. Computer Science, anticipated graduation 2020.\\
  \textbf{Stuyvesant HS} : Stuyvesant Diploma 2016;
  Relevant Coursework: AP CS, Software Development.

  \noindent{\large \textbf{Programming Experiences}}
  \vspace{0.1cm} \hrule \vspace{0.2cm}
  \noindent\textbf{HULEDET}\textit{ Full-Stack Developer} \hfill Summer 2016\\
  Startup Company to serve customers
  \begin{itemize}[label={--},noitemsep, topsep=0pt]
    \item PHP Wordpress website hosted on IPower with a MySQL backend - refactored nonworking code and fixed frontend issues.
  \end{itemize}
  \noindent\textbf{Nutritrades}\textit{ Backend and Middleware Developer} \hfill April 2016\\
  Project for ``Dream it. Code it. Win it'' 2016, Currently finalist in their competition.
  \begin{itemize}[label={--},noitemsep, topsep=0pt]
    \item Created a website hosted in Node.js and DigitalOcean that allowed users to post and sell produce they grew themselves.
  \end{itemize}
  \textbf{ELWire}\textit{ Arduino Board Programming} \hfill March 2016\\
  Programmed 5 electrical suits with strobes and patterns for our school\'s annual ``Sing!'' performance in C++.
  \begin{itemize}[label={--},noitemsep, topsep=0pt]
    \item Set timings for 5 suits to coincide with a musical number using Arduino and several EL Sequencing boards.
  \end{itemize}
  \textbf{Picky}\textit{ Backend Developer} \hfill November 2015\\ ``DefHacks()'', a hackathon hosted by CSTUY, our project won award for Best Design.
  \begin{itemize}[label={--},noitemsep, topsep=0pt]
    \item Programmed an app hosted in Python Flask and accessed Yelp's REST API that generated a list of restaurants based on what the user did NOT want to eat.
  \end{itemize}
  \textbf{DandD}\textit{ Full Stack Developer} \hfill January-February 2016\\
  Software Development Final Project.
  \begin{itemize}[label={--},noitemsep, topsep=0pt]
    \item Written with Python Flask and Mongodb, allowed users to customize their organization of information in a database.
  \end{itemize}
  \noindent\textbf{Safety in Numbers}\textit{ Backend Developer} \hfill April 2015\\
  Project for ``Dream it. Code it. Win it.'' a competition held by MIT, won the May 2015 Microsoft Prize.
  \begin{itemize}[label={--},noitemsep, topsep=0pt]
    \item Developed a webpage using Java Server Pages that assigned police precincts a general safety rating based on the city's crime data.
  \end{itemize}


  \noindent {\large \textbf{Work/Volunteer Experience}}
  \vspace{0.1cm} \hrule \vspace{0.2cm}
  \noindent\textbf{Brooklyn Public Library Central Branch}\textit{ Foreign Language Volunteer}
  \hfill Summer 2014\\
  Work consisted mainly of collaborating with other employees to relabel and reshelve books.
  \begin{itemize}[label={--},noitemsep, topsep=0pt]
    \item Worked under a supervisor and became close friends.
  \end{itemize}
  \noindent\textbf{HULEDET}\textit{ Intern }
  \hfill Summer 2016\\
  Work consisted mainly of fixing broken code and refactoring into an OOP style.
  \begin{itemize}[label={--},noitemsep, topsep=0pt]
    \item Worked alongside the founder and learned PHP and MySQL.
  \end{itemize}


  % \noindent{\large \textbf{Programming Skills} }
  % \vspace{0.1cm} \hrule \vspace{0.3cm}
  % \noindent
  % \textbf{Javascript} \textit{Full Stack Usage}
  % \begin{itemize}[label={--},noitemsep, topsep=0pt]
  %   \item Language of choice, most experience in this language.
  %   \item Well-versed in Node.js webservers and jQuery / d3 HTML based scripting.
  % \end{itemize}
  % \textbf{Python}\textit{ Full Stack Usage}
  %   - Written webservers and responsive webpages in Python Flask.\\
  % \textbf{HTML, CSS} \textit{ Frontend Usage}
  %   - Long-term experience, generated pages for projects and applications.\\
  % \textbf{Mongodb}\textit{ Backend Development} - Fluent
  % in working with this alongside Nodejs and Python.\\
  % \textbf{ Java, C/C++} \textit{ Familiar with Syntax} - Learned while deciding where to start programming.
  % \end{itemize}

  \noindent{\large \textbf{Skills/Interests}}
  \vspace{0.1cm} \hrule \vspace{0.2cm}
  \noindent\textbf{Computer Languages}\textit{ In order of fluency}:
  JavaScript, Python, Java, Latex, C/C++, Ruby.\\
  \textbf{Violin}: Practicing since age 4, held position of concertmaster in my local orchestra for 2 years.\\
  \noindent\textbf{Language}: Fluent in Mandarin Chinese\\
  \textbf{Flow Arts}: Performing Poi and Contact Juggling for 2 years.\\
\end{document}
